Checkerboards And Missing Species Combinations: Are Ecological Communities

### 2016-01-25 ManuscriptMarkDown.Rmd
Added heat map figures

In one of his assembly rules, Diamond proposed that some pairs of species were such strong competitors that they never occured together on the same island, forming a "checkerboard distribution". For example, from the matrix above, we notice that the species in rows 3 and 6 (x and y) form a checkerboard pair and never co-occur:

### Figure 2 here

>>>>

In one of his assembly rules, Diamond proposed that some pairs of species were such strong competitors that they never occured together on the same island, forming a "checkerboard distribution". For example, from the matrix above, we notice that the species in rows 8 and 10 (*Loxigilla noxis* and *Tiara olivacea*) form a checkerboard pair and never co-occur:

```{r}
m <- melt(dataWiFinches[c(8,10),])
m <- as.data.frame(cbind(rep(1:2,19),rep(1:19,each=2),m$value))

The data can be organized into a two-way contingency table:

```{r echo=FALSE}
Mychecker <- dataWiFinches[c(8,10),-1]
Mychecker <- as.matrix(Mychecker)
MyCon <- matrix(0,nrow=2,ncol=2, dimnames = list(c("A_pres","A_abs"),c("B_pres","B_abs")))
MyCon[1,1] <- sum(Mychecker[1,]==1 & Mychecker[2,]==1)
MyCon[1,2] <- sum(Mychecker[1,]==1 & Mychecker[2,]==0)
MyCon[2,1] <- sum(Mychecker[1,]==0 & Mychecker[2,]==1)
MyCon[2,2] <- sum(Mychecker[1,]==0 & Mychecker[2,]==0)
(MyCon)
```

and a Fisher's exact test yields (
### Figure 2 here
